SatWins: A Sat-based tool to Optimal Instantiations of Abstract Workflows

### 2010-01-25 publicaciones/demo_eswc10/paperdemo.tex
algunas correcciones que le hice

In this paper, we describe SatWins a system that considers
 a restricted version of WIP that adopts
the Local-As-View (LAV) approach \cite{levy:bucket} to specify the semantics of the concrete services as views of abstract services; this representation is similar to the
one that is semi-automatically generated for the DEIMOS system
\cite{AmbiteISWC09}. Additionally,  abstract workflows correspond  to conjunctive
queries on the abstract services, and  the quality
of an instantiation is an overall utility function that combine the
different QoS parameters of the selected concrete services.
In this version of WIP, the rules that define workflows (conjunctive queries)
and concrete services (views) are created in a way that all the 
functional restrictions on pre- and post-conditions of services
and their combinations are satisfied, and the QoS measures are
represented by annotating each concrete service description with
a real number that represent the overall QoS utility of the service.

In addition to provide a novel approach to describe the WIP problem, SATWins is able to  efficiently identify an abstract workflow instantiations. 
Given a WIP, a logical theory is constructed such that each model of
the theory encodes a valid instantiation, and thus all valid instantiations
are obtained by enumerating all models of the theory. This enumeration
can be efficiently performed if the logical theory is in a certain 
normal form called deterministic and decomposable negation normal
form (d-DNNF) \cite{darwiche:d-dnnfs}. Thus, the approach consists in
transforming (called compiling in the field of knowledge compilation)
the logical theory into d-DNNF format for enumerating its models efficiently; also, the  enumeration 
the best ranked models can also be performed efficiently on d-DNNF and the complexity is independent of the utility function used to rank the optimal instantiation.

In this demonstration, we  attempt to show the following key aspects of the approach implemented by SATWins. We will use a real-world example based on a simple flight-information system.
\begin{itemize}
\item We show the expressiveness of representing concrete services as views on abstract services.
\item We demonstrate the performance of the proposed techniques by computing the optimal instantiation of a given WIP in terms of different utility functions.  
\item We show the scalability of our solution by demonstrating how SATWins is able to enumerate e realistic instances of the problem in less of one second.
\end{itemize}

\section{SatWins Architecture}
 The SatWins architecture  is comprised of a Catalog of service descriptions,
the Encoder, the compiler c2d, the best model Finder, and the Decoder.
Figure~\ref{fig:architecture} depicts the overall architecture of the system.
In this framework, an instance of Workflow Instantiation Problem is defined as an
abstract workflow represented by a conjunctive query on abstract services which
is given as input together with a set set of concrete services defined by views
of abstract services.

@@

\section{Demonstration Use Cases}
In this demonstration, we will go through the different steps of the proposed approach. We illustrate our approach on  a simple flight-information system which contains information
about flights between cities and information about which cities are in
the US. Such a system can be described using LAV with the two abstract
services $\flight(x,y)$ and $\UScity(x)$. The former relates two cities
$x$ and $y$ if there is a direct flight between them, and the latter tells
whether $x$ is a US city or not. We also consider different sets of concrete services; functionality, complexity and size will be changed during the demonstration to show expressiveness, performance and scalability of our approach. An example of some of the concrete services to be used is as follows:
\begin{enumerate}[--]
\item $\national(x,y)$ relates two US cities that are connected by a direct flight,
\item $\oneway(x,y)$ relates two cities that are connected by a one-way flight,
\item $\onestop(x,y)$ relates two cities that are connected by a one-stop flight,
\item $\flightPA(x)$ tells if there is a direct flight from $x$ to Paris,
\item $\onestopPA(x,y)$ relates $x$ and $y$ if there is a flight from $x$ to Paris
      with a stop at $y$, and
\item $\fromNY(x)$ tells if there is a flight from New York into $x$.
\end{enumerate}
The descriptions of these concrete services using the abstract services:
\begin{alignat*}{1}
\national(x,y)\   &\qrule\ \flight(x,y),\,\UScity(x),\,\UScity(y)\,. \\
\oneway(x,y)\     &\qrule\ \flight(x,y)\,. \\
\onestop(x,z)\    &\qrule\ \flight(x,y),\,\flight(y,z)\,. \\
\flightPA(x)\     &\qrule\ \flight(x,\PA)\,. \\
\onestopPA(x,y)\  &\qrule\ \flight(x,y),\,\flight(y,\PA)\,. \\
\fromNY(x)\       &\qrule\ \flight(\NY,x)\,.
\end{alignat*}

@@

Using this domain, we will demonstrate the following scenarios:
\begin{itemize}
\item To show the scalability of the proposed approach, we use the behavior of SATWins in three different benchmarks. In all the cases, we show time for compilation, size of the  d-DNNF, and time to enumerate all the models as well as the optimal one. We start with a benchmark of instances for workflows with 2 to 5 sub-goals and sets of 10 to 100 concrete services. Although, the observed time suggests a sub-exponential behavior,  in any case, the results
show good performance. For instance, sets of 100
airlines with 5-stop flights can be compiled in 328 seconds; the size in disk of the d-DNNF is 3.4Mb;
the best model can be computed in 0.29 seconds, and the enumeration of all models in 0.47 seconds.
Then, in an attempt to induce an exponential growth in the compilation time, we add a second concrete service for each airline and we will show that SATWins behavior remains similar. Finally, we  involve concrete services with multiple sub-goals which are randomly generated.  The compilation time for these instances does not grow monotonically
since they are randomly generated. The same happens for the size of
the theories and the number of models. For example, the d-DNNF for 
a problem with 45 views each with 5 sub-goals is of size 5.1Mb and has
$1.26\times 10^8$ models. The time to find the best model for
this d-DNNF is 0.46 seconds while the time to enumerate all models
is about 17 hours.
\item To show the performance of the approach and reusability of existing d-DNNF, we will allow users to choose different utility metrics to compute the best solution.  We will show that the existing d-DNNF can be used to compute the best model with different utility functions, while the execution time remains the same for the different functions. 
\end{itemize}

>>>>

In this paper, we describe SatWins a system that considers
 a restricted version of WIP that adopts
the Local-As-View (LAV) approach \cite{levy:bucket} to specify the semantics of the concrete services as views of abstract services; this representation is similar to the
one that is semi-automatically generated for the DEIMOS system
\cite{AmbiteISWC09}. Additionally,  abstract workflows correspond  to conjunctive
queries on the abstract services, and  the quality
of an instantiation is an overall utility function that combines the
different QoS parameters of the selected concrete services.
In this version of WIP, the rules that define workflows (conjunctive queries)
and concrete services (views) are created in a way that all the 
functional restrictions on pre- and post-conditions of services
and their combinations are satisfied, and the QoS measures are
represented by annotating each concrete service description with
a real number that represents the overall QoS utility of the service.

In addition to providing a novel approach to describe the WIP problem, SATWins is able to  efficiently identify an abstract workflow's instantiations. 
Given a WIP, a logical theory is constructed such that each model of
the theory encodes a valid instantiation, and thus all valid instantiations
are obtained by enumerating all models of the theory. This enumeration
can be efficiently performed if the logical theory is in a certain 
normal form called deterministic and decomposable negation normal
form (d-DNNF) \cite{darwiche:d-dnnfs}. Thus, the approach consists in
transforming (called compiling in the field of knowledge compilation)
the logical theory into d-DNNF format for enumerating its models efficiently; also, the  enumeration  of
the best ranked models can also be performed efficiently on a theory in d-DNNF and
the complexity is independent of the utility function used to rank the optimal instantiation.

In this demonstration, we  attempt to show the following key aspects of the approach implemented by SATWins. We will use a real-world example based on a simple flight-information system.
\begin{itemize}
\item We show the expressiveness of representing concrete services as views on abstract services.
\item We demonstrate the performance of the proposed techniques by computing the optimal instantiation of a given WIP in terms of different utility functions.  
\item We show the scalability of our solution by demonstrating how SATWins is able to enumerate realistic instances of the problem in less than one second.
\end{itemize}

\section{SatWins Architecture}
 The SatWins architecture  is comprised of a Catalog of service descriptions,
the Encoder, the compiler c2d, the best model Finder, and the Decoder.
Figure~\ref{fig:architecture} depicts the overall architecture of the system.
In this framework, an instance of the Workflow Instantiation Problem is defined as an
abstract workflow represented by a conjunctive query on abstract services which
is given as input together with a set of concrete services defined by views
of abstract services.

@@

\section{Demonstration Use Cases}
In this demonstration, we will go through the different steps of the proposed approach.
We illustrate our approach on  a simple flight-information system which contains information
about flights between cities and information about which cities are in
the US. Such a system can be described using LAV with the two abstract
services $\flight(x,y)$ and $\UScity(x)$. The former relates two cities
$x$ and $y$ if there is a direct flight between them, and the latter tells
whether $x$ is a US city or not. We also consider different sets of concrete services; functionality, complexity and size will be changed during the demonstration to show
the expressiveness, performance and scalability of our approach. An example of some of the concrete services to be used is as follows:
\begin{enumerate}[--]
\item $\national(x,y)$ relates two US cities that are connected by a direct flight,
\item $\oneway(x,y)$ relates two cities that are connected by a one-way flight,
\item $\onestop(x,y)$ relates two cities that are connected by a one-stop flight,
\item $\flightPA(x)$ tells if there is a direct flight from $x$ to Paris,
\item $\onestopPA(x,y)$ relates $x$ and $y$ if there is a flight from $x$ to Paris
      with a stop at $y$, and
\item $\fromNY(x)$ tells if there is a flight from New York into $x$.
\end{enumerate}
The descriptions of these concrete services using the abstract services:
\begin{alignat*}{1}
\national(x,y)\   &\qrule\ \flight(x,y),\,\UScity(x),\,\UScity(y)\,. \\
\oneway(x,y)\     &\qrule\ \flight(x,y)\,. \\
\onestop(x,z)\    &\qrule\ \flight(x,y),\,\flight(y,z)\,. \\
\flightPA(x)\     &\qrule\ \flight(x,\PA)\,. \\
\onestopPA(x,y)\  &\qrule\ \flight(x,y),\,\flight(y,\PA)\,. \\
\fromNY(x)\       &\qrule\ \flight(\NY,x)\,.
\end{alignat*}

@@

Using this domain, we will demonstrate the following scenarios:
\begin{itemize}
\item To show the scalability of the proposed approach, we use the behavior of
SATWins in three different benchmarks. In all the cases, we show time for
compilation, size of the  d-DNNF, and time to enumerate all the models as well
as the optimal one. We start with a benchmark of instances for workflows with 2
to 5 sub-goals and sets of 10 to 100 concrete services. Although the observed
time suggests a sub-exponential behavior, in any case, the results
show good performance. For instance, sets of 100
airlines with 5-stop flights can be compiled in 328 seconds; the size in disk of the d-DNNF is 3.4Mb;
the best model can be computed in 0.29 seconds, and the enumeration of all models in 0.47 seconds.
Then, in an attempt to induce an exponential growth in the compilation time, we add a second concrete service for each airline and we will show that SATWins behavior remains similar. Finally, we  involve concrete services with multiple sub-goals which are randomly generated.  The compilation time for these instances does not grow monotonically
since they are randomly generated. The same happens for the size of
the theories and the number of models. For example, the d-DNNF for 
a problem with 45 views each with 5 sub-goals is of size 5.1Mb and has
$1.26\times 10^8$ models. The time to find the best model for
this d-DNNF is 0.46 seconds while the time to enumerate all models
is about 17 hours.
\item To show the performance of the approach and reusability of existing d-DNNF, we will allow users to choose different utility metrics to compute the best solution.  We will show that the existing d-DNNF can be used to compute the best model with different utility functions, while the execution time remains the same for the different functions. 
\end{itemize}
